MSD panels 1, 2 and 3 HVE Sup

### 2016-08-23 MSD_panels_1_2_3_HVE_sup_analysis.Rmd
multiplied the concentrations by 2 to get an estimate of stock concentration of the sups

## Plots of analyte concentrations

Black points show the means.

@@

>>>>

## Plots of analyte concentrations
These samples were diluted 1:2 so I multiplied the concentrations by 2 to estimate the stock concentration of the supernatents. Black points show the means.

@@

#I'm going to make a column for estimated stock concentration by multiplying the avgConc by 2(since I did a 1:2 dilution on the samples) so I can better compare with the HVE sup concentrations.

avgConc_HVE_all_panels_noStds_1to2_noBelow_fullSet <- avgConc_HVE_all_panels_noStds_1to2_noBelow_fullSet %>%
  mutate (Estimated_Stock_Conc = avgConc * 2)
